---
title: "DATA607 - Web API"
author: "Nicholas Kunze"
date: "2024-03-31"
output:
  html_document:
    highlight: pygments
    theme: cerulean
    toc: true
    toc_float: true
  pdf_document: default
editor_options: 
  chunk_output_type: console
params:
  key: "9nfmnivLAXo5vqHyhoeuGduG3cGS6BLl"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
if("RCurl" %in% rownames(installed.packages()) == FALSE) {install.packages("RCurl")}
library(RCurl)
if("jsonlite" %in% rownames(installed.packages()) == FALSE) {install.packages("jsonlite")}
library(jsonlite)
if("tidyverse" %in% rownames(installed.packages()) == FALSE) {install.packages("tidyverse")}
library(tidyverse)
```

## Overview

This assignment illustrates the ability to get and process data from REST APIs, which usually use JSON format for the payload/body.

## NYT HTTP GET

I've signed up on the dev NYT website and obtained an API key, which im storing in my parameter variables. Now I can make an HTTP GET request to access the data,

```{r api-get}
electionArticles <- fromJSON(paste0("https://api.nytimes.com/svc/search/v2/articlesearch.json?q=election&api-key=",params$key))
articlesdf <- as.data.frame(electionArticles)
class(articlesdf)
```

There appear to be nested dataframes as well, such as the headlines.

```{r nested-df}
head(articlesdf$response.docs.headline$main)
```
